%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

\newcommand{\commasep}{
	\hspace{2mm},\hspace{2mm}
}

\usepackage{my_personal_info}
\usepackage{enumitem}

% Prevent hypenating word at line break
\hyphenation{educators}
\hyphenation{merging}
\hyphenation{downloads}
\hyphenation{performs}
\hyphenation{platforms}
\hyphenation{Noggin}
\hyphenation{Sunday}
\hyphenation{immersive}
\hyphenation{designed}
\hyphenation{Android}
\hyphenation{services}
\hyphenation{eCommerce}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------
% \begin{center}
%     \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{\myname} \MakeUppercase{\mysurname}}}} {\huge\textcolor{white}{\textbf{, {\myqualification}}}}}  % First name
% 	% \colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{\mysurname}}}}} % Last name
 
%     % {\fontsize{36}{36}\selectfont\interthin FANCY\interheavy ROVER} \\ \bigskip
%     {\color{icnclr}\faEnvelope[regular]} \href{mailto:hi@example.com}{fancy@rover.com} $|$ 
%     {\color{icnclr}\faIcon{mobile-alt}} \href{tel:1234567890}{123 456 7890} $|$
%     {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/}{linkedin.com/in/fancy\_rover}
% \end{center}
\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{\myname}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{\mysurname}}}}{\huge\textcolor{white}{\textbf{, {\myqualification}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Lead/Senior Android Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{\href{http://maps.google.com/?q=\mymapaddress}{\mymapaddress}}\\
	\icon{Phone}{12}{\mymobile}\\
	\icon{At}{12}{\href{mailto:\myemail}{\myemail}}\\
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{12}{\href{\mygithuburl}{\mygithubname}}\\
	\icon{Linkedin}{12}{\href{\mylinkedinurl}{\mylinkedinname}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

%\cvsect{Who Am I?}

%\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
%	\lorem \lorem \lorem \lorem \lorem\\ % Dummy text
%\end{minipage}
%\hfill % Whitespace between
%\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
%	\vspace{-\baselineskip} % Required for vertically aligning minipages
%	\begin{barchart}{5.5}
%		\baritem{JavaScript}{60}
%		\baritem{PHP}{100}
%		\baritem{SASS/LESS}{70}
%		\baritem{Bootstrap}{70}
%		\baritem{Git}{40}
%		\baritem{LaTeX}{60}
%	\end{barchart}
%\end{minipage}

%\begin{center}
%	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
%\end{center}

%----------------------------------------------------------------------------------------
%	PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\cvsect{Professional summary}
\parentryBasic{
        Accomplished Mobile Developer with 14 years of Android experience. Delivered multiple successful apps across a variety of fields, from e-commerce and edutainment to smart devices. Well practiced and highly skilled in Kotlin, Java, and the Jetpack libraries.
    }

%----------------------------------------------------------------------------------------
%	Expertise
%----------------------------------------------------------------------------------------

\cvsect{Expertise}

\begin{minipage}[t]{0.28\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\texttt{Kotlin}\\
	\texttt{Java}\\
	\texttt{Javascript}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.28\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
		
	\texttt{Android TV}\\
	\texttt{Coroutines, Flow}\\
	\texttt{rxJava}\\
	
\end{minipage}
\hfill
\begin{minipage}[t]{0.28\linewidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
		
	\texttt{Dagger, Hilt}\\
	\texttt{Room}\\
	\texttt{Retrofit, OkHttp, Ktor}\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.08\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
		
	\texttt{Compose}\\
	\texttt{MVVM}\\
	\texttt{MVI}\\
\end{minipage}


%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}
\begin{entrylist}
	\entry
		{2/2021 -- present\\\footnotesize{contract}}
		{Noggin, Paramount {\normalfont\small - USA, remote}}
		{Senior Android Developer}
        {
            Noggin, a division of multinational mass media and entertainment conglomerate Paramount, is a preschool edutainment subscription service which provides a library of videos, ebooks, and educational games.
            \begin{itemize}[nosep, leftmargin=*]
                \item Won \textit{Best Learning App - Branded} at the 2024 Kidscreen Awards.
                \item Picked from the original app's development team to develop the new more immersive version of the app.
                \item Establish coding standards and architectural patterns.
                \item Implement video playback and casting functionality.
                \item Maintain the functionality and performance of the TV apps, ensuring seamless user experiences.
            \end{itemize}
            \texttt{Android}\pipesep\texttt{Android TV}\pipesep\texttt{Kotlin}\pipesep\texttt{Dagger}\pipesep\texttt{rxJava}\pipesep\texttt{Coroutines}\pipesep\texttt{Compose}
        }
        
	\entry
		{2/2021 -- present\\\footnotesize{contract}}
		{Learning Tapestry {\normalfont\small -- USA, remote}}
		{Android Consultant}
		{
            Provides innovation and infrastructure solutions to support learners and educators. 
            \begin{itemize}[nosep, leftmargin=*]
                \item Consult Paramount's Noggin app on using Learning Tapestry's services to drive their creation of learning experiences.
            \end{itemize}
        }
        
	\entry
		{2/2021 -- present\\\footnotesize{freelance}}
		{TopTal {\normalfont\small -- USA, remote}}
		{Android Developer}
		{
            A global, exclusive freelancing platform for the top 3\% of talent.
        }
        
	\entry
		{8/2020 -- 1/2021\\\footnotesize{contract}}
		{Teamwork {\normalfont\small -- Ireland, remote}}
		{Senior Android Developer}
		{
            Task management and team collaboration software.
            \begin{itemize}[nosep, leftmargin=*]
                \item Developed the new Teamwork project management app, an enhanced native Android rewrite of the original cross-platform version.
            \end{itemize} 
            \texttt{Android}\pipesep\texttt{Kotlin}\pipesep\texttt{Dagger}\pipesep\texttt{rxJava}
        }
        
    \entry
		{4/2016 --- 7/2020\\\footnotesize{full time}}
		{Flat Circle {\normalfont\small -- Cape Town, South Africa}}
		{Lead Android Developer}
		{
            Mobile development agency aquired by TFG Labs in 2021.
            \begin{itemize}[nosep, leftmargin=*]
                \item Establish coding standards and architectural patterns.
                \item Led a team of developers, providing mentorship and guidance to foster professional growth and enhance technical skills.
                \item Consistently delivered multiple apps on time, ensuring reliability and optimal performance: 
                \begin{itemize}
                    \item \textbf{Blueair} controls award winning, Swedish, smart air purifiers.
                    \item \textbf{Kin} plans, tracks, splits and settles shared expenses.
                    \item \textbf{TimesLIVE} and \textbf{Times Select} are digital versions of big South African news publications.
                    \item \textbf{Picup driver's app} connects driver with available deliveries, where it performs navigation and package tracking.
                \end{itemize}
            \end{itemize}
    		\texttt{Android}\pipesep\texttt{Android TV}\pipesep\texttt{Android Wear}\pipesep\texttt{Kotlin}\pipesep\texttt{Java}\pipesep\texttt{rxJava}
        }
  
	\entry
		{7/2015 --- 3/2016\\\footnotesize{full time}}
		{Spree, Media24 {\normalfont\small -- Cape Town, South Africa}}
		{Senior Android Developer}
		{
            A fashion e-commerce website with a “magazine-styled shopping experience” -- merged with Superbalist in 2018.
            \begin{itemize}[nosep, leftmargin=*]
                \item Established coding standards and architectural patterns as the sole Android developer.
                \item Released app a month ahead of schedule - resulting in considerable downloads and conversion rates on Black Friday, which the original schedule would have missed.
            \end{itemize}
            \texttt{Android}\pipesep\texttt{Groovy}
        }
        
	\entry
		{2/2015 --- 5/2015\\\footnotesize{freelance}}
		{Flat Circle {\normalfont\small -- Cape Town, South Africa}}
		{Android Consultant}
        {
            Mobile development agency acquired by TFG Labs in 2021. 
            \begin{itemize}[nosep, leftmargin=*]
                \item Consulted and initiated development on the Android launcher and media player used on the \textit{Marshall London Android phone}.
                \item The London phone is “one of the best low-end phones we've seen.” according to \textit{The Verge}.
            \end{itemize}
    		\texttt{Android}\pipesep\texttt{Java}
        }
        
	\entry
		{12/2013 -- 6/2015\\\footnotesize{full time}}
		{Takealot {\normalfont\small -- Cape Town, South Africa}}
		{Senior Mobile Developer}
		{
            South Africa's largest online retailer.
            \begin{itemize}[nosep, leftmargin=*]
                \item Overhauled Takealot's outdated, outsourced Android app - now consistently rated in the top 5 (in SA) for shopping on the Play Store.
                \item Developed the new mobile site which won \textit{Best eCommerce Mobile Site} Award at SA's eCommerce Awards 2015.
            \end{itemize}
            \texttt{Android}\pipesep\texttt{Java}\pipesep\texttt{web}\pipesep\texttt{Javascript}
        }
  
	\entry
		{4/2010 -- 11/2013\\\footnotesize{full time}}
		{Virtual Mobile Technologies {\normalfont\small -- Cape Town, South Africa}}
		{Senior Software Developer}
		{
            VMT's product Ramp was a mobile enterprise application platform aimed at managing a complete enterprise environment to build and deploy secure, native apps across multiple platforms.
            \begin{itemize}[nosep, leftmargin=*]
                \item Developed and maintained Ramp virtual machines for multiple platforms, e.g. Android, iOS, Windows Phone, Blackberry, etc.
            \end{itemize}
            \texttt{Android}\pipesep\texttt{Java}\pipesep\texttt{iOS}\pipesep\texttt{Objective-C}\pipesep\texttt{Javascript}\pipesep\texttt{Windows Phone}\pipesep\texttt{C\#}\pipesep\texttt{BlackBerry}
        }
 
	\entry
		{1/2007 -- 3/2010\\\footnotesize{full time}}
		{Perceive {\normalfont\small -- Cape Town, South Africa}}
		{Senior Software Developer}
		{
            Provider of intelligent surveillance solutions to various security concerns. 
            \begin{itemize}[nosep, leftmargin=*]
                \item Developed the surveillance system's monitor application.
                \item Assisted in the development of various surveillance algorithms, e.g. human detection and fall detection.
            \end{itemize}
            \texttt{Python}\pipesep\texttt{OpenCV}\pipesep\texttt{NumPy}
        }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\parentry
    {Master of Science in Engineering (MScEng) in Applied Mathematics {\normalfont\small -- cum laude}}
    {Stellenbosch University}
    {
        Thesis: \textit{"Metric reconstruction of multiple rigid bodies"} -- a structure from motion (SfM) system that reconstructs, from a video or photo sequence, the 3D structure and motion of multiple rigid bodies. The reconstruction is identical up to a similarity transformation and assumes a projective camera model with optional provision for camera calibration.
    }
    
\parentry
    {Bachelor of Science with Honours (BScHons) in Computer Science}
    {Stellenbosch University}
    {}

\parentry
    {Bachelor of Science (BSc) in Mathematical Science}
    {Stellenbosch University}
    {Majored in Computer Science and Applied Mathematics.}

%----------------------------------------------------------------------------------------

\end{document}
